---
output: github_document
---

  <!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, warning = FALSE, messsage = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  error = TRUE,
  dpi = 200,
  out.width = "100%",
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# `tidyBF`: Tidy Wrapper for 'BayesFactor' Package

[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0.9000-orange.svg?style=flat-square)](https://github.com/IndrajeetPatil/tidyBF/commits/master)
[![Daily downloads badge](https://cranlogs.r-pkg.org/badges/last-day/tidyBF?color=blue)](https://CRAN.R-project.org/package=tidyBF)
[![Weekly downloads badge](https://cranlogs.r-pkg.org/badges/last-week/tidyBF?color=blue)](https://CRAN.R-project.org/package=tidyBF)
[![Monthly downloads badge](https://cranlogs.r-pkg.org/badges/last-month/tidyBF?color=blue)](https://CRAN.R-project.org/package=tidyBF)
[![Total downloads badge](https://cranlogs.r-pkg.org/badges/grand-total/tidyBF?color=blue)](https://CRAN.R-project.org/package=tidyBF)
[![Travis Build Status](https://travis-ci.org/IndrajeetPatil/tidyBF.svg?branch=master)](https://travis-ci.org/IndrajeetPatil/tidyBF) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/IndrajeetPatil/tidyBF?branch=master&svg=true)](https://ci.appveyor.com/project/IndrajeetPatil/tidyBF) 
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![DOI](https://zenodo.org/badge/126624251.svg)](https://zenodo.org/badge/latestdoi/126624251)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/IndrajeetPatil/tidyBF/commits/master)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)
[![Coverage Status](https://img.shields.io/codecov/c/github/IndrajeetPatil/tidyBF/master.svg)](https://codecov.io/github/IndrajeetPatil/tidyBF?branch=master)
[![Coverage Status](https://coveralls.io/repos/github/IndrajeetPatil/tidyBF/badge.svg?branch=master)](https://coveralls.io/github/IndrajeetPatil/tidyBF?branch=master)

# Overview

`tidyBF` package is a tidy wrapper around `BayesFactor` package that always
expects the data to be in the tidy format and return a tibble containing Bayes
Factor values. Additionally, it provides a more consistent syntax and by
default returns a dataframe with rich details. These functions can also return
expressions containing results from Bayes Factor tests that can then be
displayed on custom plots.

# Installation

To get the latest, stable `CRAN` release:

```{r installation1, eval = FALSE, warning = FALSE, messsage = FALSE}
install.packages(pkgs = "tidyBF")
```

You can get the **development** version of the package from `GitHub`. To see
what new changes (and bug fixes) have been made to the package since the last
release on `CRAN`, you can check the detailed log of changes here:
<https://indrajeetpatil.github.io/tidyBF/news/index.html>

If you are in hurry and want to reduce the time of installation, prefer-

```{r installation2, eval = FALSE, warning = FALSE, messsage = FALSE}
# needed package to download from GitHub repo
install.packages(pkgs = "remotes")

remotes::install_github(
  repo = "IndrajeetPatil/tidyBF", # package path on GitHub
  quick = TRUE # skips docs, demos, and vignettes
)
```

If time is not a constraint-

```{r installation3, eval = FALSE, warning = FALSE, messsage = FALSE}
remotes::install_github(
  repo = "IndrajeetPatil/tidyBF", # package path on GitHub
  dependencies = TRUE, # installs packages which `tidyBF` depends on
  upgrade_dependencies = TRUE # updates any out of date dependencies
)
```

# Benefits

Below are few concrete examples of where `tidyBF` wrapper might provide a more
friendly way to access output from or write functions around `BayesFactor`.

## Syntax consistency

`BayesFactor` is inconsistent with its formula interface. `tidyBF` avoids this
as it doesn't provide the formula interface for any of the functions.

```{r formula}
# setup
set.seed(123)

# with `BayesFactor` ----------------------------------------
suppressPackageStartupMessages(library(BayesFactor))
data(sleep)

# independent t-test: accepts formula interface
ttestBF(formula = wt ~ am, data = mtcars)

# paired t-test: doesn't accept formula interface
ttestBF(formula = extra ~ group, data = sleep, paired = TRUE)

# with `tidyBF` ----------------------------------------
library(tidyBF)

# independent t-test
bf_ttest(data = mtcars, x = am, y = wt)

# paired t-test
bf_ttest(data = sleep, x = group, y = extra, paired = TRUE)
```

## Expressions for plots

Although all functions default to returning a dataframe, you can also use it
to extract expressions that can be displayed in plots.

```{r expr_plot}
# setup
set.seed(123)
library(ggplot2)

# two-sample t-test results in an expression
stats_exp <- bf_ttest(mtcars, am, wt, output = "alternative")

# using the expression to display details in a plot
ggplot(mtcars, aes(as.factor(am), wt)) +
  geom_boxplot() +
  labs(subtitle = stats_exp)
```

## Dataframe with all the details

`BayesFactor` can return the Bayes Factor value corresponding to either
evidence in favor of the null hypothesis over the alternative hypothesis
(`BF01`) or in favor of the alternative over the null (`BF10`), depending on how this
object is called. `tidyBF` on the other hand return both of these values and
their logarithms.

```{r all_together}
# `BayesFactor` object
bf <- BayesFactor::correlationBF(y = iris$Sepal.Length, x = iris$Petal.Length)

# alternative
bf

# null
1 / bf

# `tidyBF` output
bf_corr_test(iris, Sepal.Length, Petal.Length, bf.prior = 0.333)
```

Note that the log-transformed values are helpful because in case of strong
effects, the raw Bayes Factor values can be pretty large, but the
log-transformed values continue to remain easy to work with.

# Code of Conduct

Please note that the `tidyBF` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
